Country-Level Impact of Education on Entrepreneurship

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

Actually, what determines entrepreneurship at a country-level has been long searched already but although structural and environmental factors have been looked at extensively, less has been done regarding cultural or educational factors. Yet, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@Freytag2007] ?????? 2010 VERSION MAIN BIB ?????. Even if “in recent years research has increasingly devoted itself to the subject” [@OECD2009], a lot still needs to be done.

@@

Of course, we also looked into other studies connecting educational features and entrepreneurship. As a matter of fact, most of the research tends to focus specifically on entrepreneurial education, whatever its form, as it is expected partly to support the entrepreneurial self-efficacy ??????? Boyd and Vosikis MAIN BIB ??????????? . One slightly different and interesting perspective is that of King and Sobel [@Kerry2008], who have already tried to show how school choice, and thus a different kind of interactions with students, can increase the rate of youth entrepreneurship but their perspective was still not directly in lign with our research design, they  asserted that a more business-like environment in K-12 education was the key, which was favoured by voucher programmes.

@@

Now, having explained how determinants of entrepreneurship have been looked into, having mentioned how education has been related to entrepreneurship so far, we need to assert here our very research design. What we expect to find out is to what extent the support of students' self-confidence within the education system impacts the rate of entrepreneurship across OECD countries.

@@

Here, when we mention that an education system reinforces self-confidence, we mean that teachers use positive reinforcement when interacting with students. This entails providing feedback that will help the students maintain their level of motivation as well as their level of self-esteem. This also entails supporting students taking initiatives, encouraging creativity.

@@

Having explained what lead us into this specific research design, we will now present our methodology for a quantitative analysis and the indicators that we used in greater detail.

>>>>

Of course, what determines entrepreneurship at a country-level has been long searched already but although structural and environmental factors have been looked at extensively, less has been done regarding cultural or educational factors. Yet, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@Freytag2007] ?????? 2010 VERSION MAIN BIB ?????. Even if “in recent years research has increasingly devoted itself to the subject” [@OECD2009], a lot still needs to be done.

@@

Eventually, this goes without saying, we also looked into other studies connecting educational features and entrepreneurship. As a matter of fact, most of the research tends to focus specifically on entrepreneurial education, whatever its form, as it is expected partly to support the entrepreneurial self-efficacy ??????? Boyd and Vosikis MAIN BIB ??????????? . One slightly different and interesting perspective is that of King and Sobel [@Kerry2008], who have already tried to show how school choice, and thus a different kind of interactions with students, can increase the rate of youth entrepreneurship but their perspective was still not directly in lign with our research design, they  asserted that a more business-like environment in K-12 education was the key, which was favoured by voucher programmes.

@@

*Research Design*

At this stage, having explained how determinants of entrepreneurship have been looked into, having mentioned how education has been related to entrepreneurship so far, we need to assert here our very research design. What we expect to find out is to what extent the support of students' self-confidence within the education system impacts the rate of entrepreneurship across OECD countries.

@@

Here, when we mention that an education system reinforces self-confidence, we mean that teachers use positive reinforcement when interacting with students. This entails providing feedback that will help the students maintain their level of motivation as well as their level of self-esteem. This also includes supporting students taking initiatives and encouraging their creativity.

@@

Having explained what lead us into this specific research design, we will now present our data sources in greater detail.
